---
title: "First trawl - Analysis 2017-PURE-SA"
output:
  pdf_document: 
number_sections: yes
toc: yes
html_document: default
---
  
```{r setup, message=FALSE, warning=FALSE, echo = FALSE}
library(dplyr)
library(memisc)
```

# Intro

This file collects some overview notes on the first trawl through the PURE dataset. Notes for our reference and for follow-up with Lanthe. 

# List of files

Received from Lanthe:

```
-rwx------ 1 sfos0247 mkpasswd 181803 Aug  1 14:19 Combined data 2005_2010.sav
-rwx------ 1 sfos0247 mkpasswd 340831 Aug  1 14:19 Combined data 2005_2010_2015.sav
-rwx------ 1 sfos0247 mkpasswd 116350 Aug  1 14:19 Demographic data 2005.sav
-rwx------ 1 sfos0247 mkpasswd  59339 Aug  1 14:19 Demographic data 2010.sav
-rwx------ 1 sfos0247 mkpasswd  26536 Aug  1 14:19 Demographic data 2015.sav
-rwx------ 1 sfos0247 mkpasswd  38732 Aug  1 14:19 Household income 2005.sav
-rwx------ 1 sfos0247 mkpasswd  31506 Aug  1 14:19 Live events_2005.sav
-rwx------ 1 sfos0247 mkpasswd  20674 Aug  1 14:19 Live events_2010.sav
-rwx------ 1 sfos0247 mkpasswd  15034 Aug  1 14:19 Live events_2015.sav
-rwx------ 1 sfos0247 mkpasswd  47545 Aug  1 14:19 Medical history_2005.sav
-rwx------ 1 sfos0247 mkpasswd  50087 Aug  1 14:19 Medical history_2010.sav
-rwx------ 1 sfos0247 mkpasswd  23945 Aug  1 14:19 Medical history_2015.sav
-rwx------ 1 sfos0247 mkpasswd  12054 Aug  1 14:19 Participant HIV status.sav
-rwx------ 1 sfos0247 mkpasswd 134948 Aug  1 14:19 Physical measurements.sav
-rwx------ 1 sfos0247 mkpasswd  25648 Aug  2 09:28 Variables of interestFINAL.docx
-rwx------ 1 sfos0247 mkpasswd      0 Aug 10 18:47 data-raw-list.txt
```

# Summary attrition rates

These are the overall rates for all three waves. Individual variables may have higher levels of missing values thoug

* Wave 1: 2010 cases. 
* Wave 2: 1263 cases (747 left the sample = `r 100*747/2010` percent )
* Wave 3: 930 cases 
    + 839 are from Wave 2  - 427 have left `r 100*427/1266` percent attrition at this stage) 
    + 91 have returned after missing Wave 2

So in total 839 cases have all three waves (out of 2010 that's `r 100*(2010-839)/2010` percent attrition overall).

# Data cleaning up and mergeing

The 14 files are partially merged, but not completely though. Additionally there are varying numebrs of cases in each file making it necessary to manually check each file before merging on the assumption of unique identifiers.

The following table summarizes the file contents as it was received. 

Clearly table 1 and 2 are already merged to some extent, but the numbers of cases are already troubling (e.g. table 1 has more cases than 3, table 2 has even more, these are obvious mistakes) so instead I start from scratch. 

```{r, echo = FALSE, results='asis', cap}
file.list.summary <- read.csv( "../data/outputs/file.list.csv")
knitr::kable(file.list.summary[,1:4], caption = 'Summary of received data files')
```

## Notes on individual file cleaning and mergeing

### Variable naming conventions
Variable names should generally follow the following conventions:

* `barcode` is the unique case identifier througout. 
* suffix `_2005` `_2010` or `_2015` indicates the wave. 
* prefix `ind` means it's an indicato variable - indicating which table/wave it came from

###`Demographic data 2005.sav` 

* One case is duplicated (2184)---I remove one occurance. 
* Ten cases are missing everything (except for location. (1011 3061 3062 3063 4122 4123 4124 4125 4453 4454)---I removed them. 

* Added indicator variable `ind.wave.1`

### `Demographic data 2010.sav` 

* There is an additional case (13020) presumably typo - removed.
* There are thirteen cases (2231  2312  2315  2325 3166  3218  3254  4161  4219  4250  4301  4381  4390) missing demographic data but not life event data? Left in for now.
* Two cases have all missing values: 3159 and 4343 - removed. 
* There are three cases (3370, 1211 and 1486) that change gender from 2005, *TODO*: figure out what to do with them, still in atm. 

* Added indicator variable `ind.wave.2`

### `Demographic data 2015.sav`   

* In 2015 files two cases are ducplicate (2258 and 2441), remove second occurence, even though 2441 has different values for `change diet`. 

* add indicator variable `ind.wave.3`


### `Household income 2005.sav` 

* Double check table 6 - income is OK already in `Demographic data 2005.sav`. (but there are 10 rows too many)

###  `Live events_2005.sav`
* Double check table 7 - `Live events_2005.sav` - same as in 3 `Demographic data 2005.sav`. 

###  `Live events_2010.sav`
* Double check table 8 - `Live events_2010.sav` - same as in 4 `Demographic data 2010.sav`.  (but there is one row too many). 

###  `Live events_2015.sav`

* Two rows duplicated (2477 3100) -- removed. 
* There are seven cases with all values missing (3038 3042 3162 3222 3231 3314 4273) - removed
* There is one case in table 9 that is not in table 5 ( 4094), removed. 

* add indicator variable `ind.wave.3.tab.9`



### Table 10 - `Medical history_2005.sav` 

* Same as 2005: case 2184 is a duplicate, and ten more  cases (1011, 3061 3062 3063 4122 4123 4124 4125 4453 4454) have everything missing. All 11 are removed. 

* add indicator variable `ind.wave.1.med.h`

### `Medical history_2010.sav` 

* Fourteen cases are duplicated 2184 2231 2312 2315 2325 3166 3218 3254 4161 4219 4250 4301 4381 4390 - removed.
* and same 11 that were already missing in 2005, removed again
* and 13020 is also removed.

* add indicator variable `ind.wave.2.med.h`

### `Medical history_2015.sav` 
* one complete duplicate 2441 - one removed
* one duplicate but with different `hypertension_2015` value - set to NA until comfirmed. 

* add indicator variable `ind.wave.3.med.h`

### `Participant HIV status.sav ` 

* Everything looks OK.

###  `Physical measurements.sav`
    
* Has two cases with completely missing all values (1090 and 1353) - removed
  
    
## Follow-up points for Lanthe

**This is essentially the same information as in the previous section---but instead of recordkeeping the idea is to get answers from Lanthe, and also to give her information that might be relevant to her.**

### Questions for follow-up for Lanthe

`Demographic data 2005.sav`:

* In `Demographic data 2005.sav` file case 1011 has missing all data. 
* In `Demographic data 2005.sav` file case 2184 is duplicated. 
* In `Demographic data 2005.sav` file cases   3061 3062 3063 4122 4123 4124 4125 4453 4454
have  missing all data except location.
* This removes 11 cases from the first wave, leaving 2010 true cases?

` Demographic data 2010.sav `:

* What is barcode # 13020 in here? (but also in `Combined data 2005_2010.sav` and ` Demographic data 2010.sav `, `Live events_2010.sav` and `  Medical history_2010.sav `)
* what is up with barcode # 3370? In  `Demographic data 2005.sav ` they are Female, in `Demographic data 2010.sav ` they are Male, in  `Demographic data 2015.sav ` they have no gender or location recorded. 
* what is up with barcode # 1211? In  `Demographic data 2005.sav ` they are Female, in `Demographic data 2010.sav ` they are Male, in  `Demographic data 2015.sav ` they are "2", which is presumably again female?
* what is up with barcode # 1486? In  `Demographic data 2005.sav ` they are Male, in `Demographic data 2010.sav ` they are Female, in  `Demographic data 2015.sav ` they are "1", which is presumably again male? 
* Additionally there are 15 variables ( 2231 2312 2315 2325 3159 3166 3218 3254 4161 4219 4250 4301 4343 4381 4390) where the demographic variables are all missing in 2010. 

` Demographic data 2015.sav `:

* In `Demographic data 2015.sav` there are two duplicate cases 2258 and 2441. 
* Furthermore one of them is not w a perfet duplicate: case 2441 has different values for `change_diet`, making this error doubly concerning. 
* Four cases (3231 4026 4136 4189) have no demographic info, although they have `change diet`, what are these?
* Just double checking, there are 539 Rural cases in 2015 - and all of them are missing demographic variables?
* **Important** when can the 539 2015 rural cases be coded? Because withtout them there is really nothing we can do?

`Household income 2005.sav`

 * Ten cases are here with no values, also don't exist in Wave.1. (1011 3061 3062 3063 4122 4123 4124 4125 4453 4454)

`Live events_2010.sav`

* One case too many 13020, this is a duplicate of 1302/1302? 

`Live events_2015.sav`

* Two duplicated cases: 2477 3100, but identical. Should be removed? 
* seven cases have all missing data (3038 3042 3162 3222 3231 3314 4273), should be removed from here?
* Case 4094 is has only two 2015 variables: `birth in family` and `death in family`, but nothing else? Was this person actually in wave three? There is no record in `Demographic data 2015.sav`?

`Medical history_2005`:

* Same 11 as in `Demographic data 2005.sav` have missing data and are removed. 

`Medical history_2010`:

* There are 14 duplicate entries here: 2184 2231 2312 2315 2325 3166 3218 3254 4161 4219 4250 4301 4381 4390, in addition to the 11 ones from 2005 that have no data. Hence 2035 rows instead of 2010 I guess. 
* also 13020 is here, which is either a duplicate of 1302 or 1320? or sth else?

`Medical history_2015`:

* There is one duplicate(2241) but there is also a duplicate (2258) which has two different values for hypertension, which is correct or do we not know?
* Also there are 31 cases with wave 3 demographic data, but no medical history data from 2015: (1016 1044 1064 1103 1230 1238 1313 1419 1425 1437 2090 2187 2255 2352 2389 2398 2400 2444 2469 3058 3103 3109 3227 3351 3382 3397 3488 4025 4062 4139 4187)

`Participant HIV status.sav `:
* all good

`Physical measurements.sav`: 
* Has two cases with completely missing all values (1090 and 1353).


### Techincal points for Lanthe - no need for follow-up
* There are two variables in `Combined data 2005_2010.sav` that are empty - this is just some artefact of merging?
* `Demographic data 2015.sav` location and gender are not labeled. 
* In  `Demographic data 2015.sav`  five cases (  2184 2258 2441 2477 3100) are duplicated
* There are 25 cases from `Demographic data 2015.sav` with missing life events `Live events_2015.sav` (1437 2378 2469 2479 3038 3042 3058 3103 3106 3109 3162 3222 3227 3231 3314 3351 3397 3410 3488 4025 4062 4139 4187 4273 4494). 



# Appendix - codebook {}

```{r, echo = FALSE,  message=FALSE, warning=FALSE, results='asis'}
require(memisc)
fd <- read.csv("../data/outputs/clean.fd.csv")
codebook(fd)
```
    