---
title: "Journal - Analysis 2017-PURE-SA"
output:
  pdf_document: 
    highlight: tango
    number_sections: yes
    toc: yes
  html_document: default
---
```{r setup, message=FALSE, warning=FALSE, echo = FALSE}
library(dplyr)
library(memisc)
```

Notes on analysis of epidemiological data from the South Africa arm of the PURE survey. 

# 4.8.2017

Went to say bye to Lanthe, got a copy of the data from Lanthe. 

Manually copied files to data/PURE/data-raw., output from `ls -1l` below:

```
-rwx------ 1 sfos0247 mkpasswd 181803 Aug  1 14:19 Combined data 2005_2010.sav
-rwx------ 1 sfos0247 mkpasswd 340831 Aug  1 14:19 Combined data 2005_2010_2015.sav
-rwx------ 1 sfos0247 mkpasswd 116350 Aug  1 14:19 Demographic data 2005.sav
-rwx------ 1 sfos0247 mkpasswd  59339 Aug  1 14:19 Demographic data 2010.sav
-rwx------ 1 sfos0247 mkpasswd  26536 Aug  1 14:19 Demographic data 2015.sav
-rwx------ 1 sfos0247 mkpasswd  38732 Aug  1 14:19 Household income 2005.sav
-rwx------ 1 sfos0247 mkpasswd  31506 Aug  1 14:19 Live events_2005.sav
-rwx------ 1 sfos0247 mkpasswd  20674 Aug  1 14:19 Live events_2010.sav
-rwx------ 1 sfos0247 mkpasswd  15034 Aug  1 14:19 Live events_2015.sav
-rwx------ 1 sfos0247 mkpasswd  47545 Aug  1 14:19 Medical history_2005.sav
-rwx------ 1 sfos0247 mkpasswd  50087 Aug  1 14:19 Medical history_2010.sav
-rwx------ 1 sfos0247 mkpasswd  23945 Aug  1 14:19 Medical history_2015.sav
-rwx------ 1 sfos0247 mkpasswd  12054 Aug  1 14:19 Participant HIV status.sav
-rwx------ 1 sfos0247 mkpasswd 134948 Aug  1 14:19 Physical measurements.sav
-rwx------ 1 sfos0247 mkpasswd  25648 Aug  2 09:28 Variables of interestFINAL.docx
-rwx------ 1 sfos0247 mkpasswd      0 Aug 10 18:47 data-raw-list.txt
```

~~Looks like "Combined data 2005_2010_2015.sav" is everything we need?~~

# 10.8.2017

Need to come up with standard variable names.

Go through `Variables of interestFINAL.docx` and prepare questions for Lanthe re data availability, and notes.


## Standard variable names

Use the ones in the .sav files, not our data request. They use undescores, but that's not a big deal.


# 11.8.2017

Prepare available variable summaries. 

## Available variables - number oof cases missing 

~~Summary table of variables and proportion missing, total N = 2025. 
(plwh(a) is shorthand for "People with HIV/Aids")~~

~~This table needs to be paired with a verision of Sara and mine variable request table, also the order here is alphabetical. ~~ I'll get back to this. 

```{r, echo = FALSE}
# dt <- read.csv("../data/outputs/combined.variables.missing.csv")
# knitr::kable(dt, digits = 2)
```

## Codebook

The summary statistics for all ~~73~~ 127 variables is in the appendix. 


# 14.8.2017

Merge our variable list with available list.. OK, realise that there are more variables than just in the 'combined file'. So will have to do a merge manually 

# 15.8.2017

Merging the data files, fourteen of them? but how can I automate this without duplicating files already joined by Lanthe?

Start `01-data-clean.R` for proper cleaning of data. 

```{r, echo = FALSE, eval = FALSE}
## I'll do this later.
rv.dt <- read.csv("../data/raw-data/requested-vars.csv")
received <- read.csv("../data/outputs/received.varnames.csv")

rv.dt %>% mutate(id = 1:nrow(rv.dt)) %>% 
  dplyr::rename(variables = VARIABLES ) %>% 
  dplyr::select(id, variables) %>% 
  mutate(year.2005 = NA, 
         year.2010 = NA,
         year.2015 = NA) %>% 
  as_tibble() %>% 
  rbind(list(0, "ID", NA, NA, NA), .) -> all.vars
all.vars[1,3:5] <- rep(received[1,2], 3)
all.vars[2,3:5] <- received[4:6,2]
all.vars[3,3:5] <- rep(received[3,2], 3)
all.vars[4,3:5] <- received[7:9,2]
all.vars[5,3:5] <- received[10:12,2]
all.vars[6,3:5] <- received[13:15,2]
all.vars[7,3:5] <- received[20:22,2]
all.vars[8,3:5] <- c(received[23,2], NA, NA)
all.vars <- rbind(all.vars, c(7.5,unlist(all.vars[8,2:5]))) %>% 
  mutate(id = as.numeric(id)) %>% arrange(id)
all.vars[9,3:5] <- received[44:46,2]

all.vars[18:28,]
received[24:35,]
```


# 16.8.2017

OK, the numbers of cases is a complete mess in these 14 files. Like have a look: 

```{r, echo = FALSE, results='asis'}
file.list.summary <- read.csv( "../data/outputs/file.list.csv")
knitr::kable(file.list.summary[,1:4])
```

So this takes essentially a whole day manually disentangling. See  Now I've got 

* Wave 1: 2010 cases. 
* Wave 2: 1265 cases (745 left the sample = `r 745/2010` percent )
* Wave 3: 926 cases 
    + 836 are from Wave 2  - 429 have left `r 745/2010` percent attrition) 
    + 90 have returned after missing Wave 2

So in total 836 cases have all three waves (out of 2010 that's `r (2010-836)/2010` percent attrition).

# 17.8.2017

Second day of cleaning up and merging. Finally finished, table here summarizes file case and variable numbers. 

```{r, echo = FALSE, results='asis'}
file.list.summary <- read.csv( "../data/outputs/file.list.csv")
knitr::kable(file.list.summary)
```

Details on what was done are in `reports/01-first.trawl.Rmd`. 

# 18.8.2017

Write up all notes on clean and merge, and follow up for Lanthe. 

Double check 01-data.clean.R is OK, and does everything I want it to do. 

Some data checking:

* age should go up five years (+/- one year) between waves. 

* never married cannot happen after married already?

# Appendix - codebook 

```{r, echo = FALSE,  message=FALSE, warning=FALSE, results='asis'}
require(memisc)
fd <- read.csv("../data/outputs/clean.fd.csv")
codebook(fd)
```