---
title: "Journal - Analysis 2017-PURE-SA"
output:
  pdf_document: default
  html_document: default
---


Notes on analysis of epidemiological data from the South Africa arm of the PURE survey. 

# 4.8.2017

Went to say bye to Lanthe, got a copy of the data from Lanthe. 

Manually copied files to data/PURE/data-raw., output from `ls -1l` below:

```
-rwx------ 1 sfos0247 mkpasswd 181803 Aug  1 14:19 Combined data 2005_2010.sav
-rwx------ 1 sfos0247 mkpasswd 340831 Aug  1 14:19 Combined data 2005_2010_2015.sav
-rwx------ 1 sfos0247 mkpasswd 116350 Aug  1 14:19 Demographic data 2005.sav
-rwx------ 1 sfos0247 mkpasswd  59339 Aug  1 14:19 Demographic data 2010.sav
-rwx------ 1 sfos0247 mkpasswd  26536 Aug  1 14:19 Demographic data 2015.sav
-rwx------ 1 sfos0247 mkpasswd  38732 Aug  1 14:19 Household income 2005.sav
-rwx------ 1 sfos0247 mkpasswd  31506 Aug  1 14:19 Live events_2005.sav
-rwx------ 1 sfos0247 mkpasswd  20674 Aug  1 14:19 Live events_2010.sav
-rwx------ 1 sfos0247 mkpasswd  15034 Aug  1 14:19 Live events_2015.sav
-rwx------ 1 sfos0247 mkpasswd  47545 Aug  1 14:19 Medical history_2005.sav
-rwx------ 1 sfos0247 mkpasswd  50087 Aug  1 14:19 Medical history_2010.sav
-rwx------ 1 sfos0247 mkpasswd  23945 Aug  1 14:19 Medical history_2015.sav
-rwx------ 1 sfos0247 mkpasswd  12054 Aug  1 14:19 Participant HIV status.sav
-rwx------ 1 sfos0247 mkpasswd 134948 Aug  1 14:19 Physical measurements.sav
-rwx------ 1 sfos0247 mkpasswd  25648 Aug  2 09:28 Variables of interestFINAL.docx
-rwx------ 1 sfos0247 mkpasswd      0 Aug 10 18:47 data-raw-list.txt
```

Looks like "Combined data 2005_2010_2015.sav" is everything we need?

# 10.8.2017

Need to come up with standard variable names.

Go through `Variables of interestFINAL.docx` and prepare questions for Lanthe re data availability, and notes.


## Standard variable names

Use the ones in the .sav files, not our data request. They use undescores, but that's not a big deal.


# 11.8.2017

Prepare available variable summaries. 

## Available variables - missing 

Summary table of variables and proportion missing, total N = 2025. 
(plwh(a) is shorthand for "People with HIV/Aids")

This table needs to be paired with a verision of Sara and mine variable request table, also the order here is alphabetical. 

```{r, echo = FALSE}
dt <- read.csv("../data/outputs/combined.variables.missing.csv")
knitr::kable(dt, digits = 2)
```

## Codebook

The summary statistics for all 73 variables is in the appendix. 



## Notes

* Cursory inspection seems to indicate the "Combined data 2005_2010_2015.sav" contains all the data the individual files do. Double check with Lanthe.

## Follow-up for Lanthe:

* Does "Combined data 2005_2010_2015.sav" contain all the data that the individual files do?



# Appendix - codebook 73 vars

Original 73 variables in original order

```{r, echo = FALSE,  message=FALSE, warning=FALSE, results='asis'}
require(memisc)
load("../data/outputs/combined.variables.codebook.RData")
combined.summary
```