---
title: "Journal - Analysis 2017-PURE-SA"
output:
  pdf_document: default
  html_document: default
---
```{r setup}
library(dplyr)

```

Notes on analysis of epidemiological data from the South Africa arm of the PURE survey. 

# 4.8.2017

Went to say bye to Lanthe, got a copy of the data from Lanthe. 

Manually copied files to data/PURE/data-raw., output from `ls -1l` below:

```
-rwx------ 1 sfos0247 mkpasswd 181803 Aug  1 14:19 Combined data 2005_2010.sav
-rwx------ 1 sfos0247 mkpasswd 340831 Aug  1 14:19 Combined data 2005_2010_2015.sav
-rwx------ 1 sfos0247 mkpasswd 116350 Aug  1 14:19 Demographic data 2005.sav
-rwx------ 1 sfos0247 mkpasswd  59339 Aug  1 14:19 Demographic data 2010.sav
-rwx------ 1 sfos0247 mkpasswd  26536 Aug  1 14:19 Demographic data 2015.sav
-rwx------ 1 sfos0247 mkpasswd  38732 Aug  1 14:19 Household income 2005.sav
-rwx------ 1 sfos0247 mkpasswd  31506 Aug  1 14:19 Live events_2005.sav
-rwx------ 1 sfos0247 mkpasswd  20674 Aug  1 14:19 Live events_2010.sav
-rwx------ 1 sfos0247 mkpasswd  15034 Aug  1 14:19 Live events_2015.sav
-rwx------ 1 sfos0247 mkpasswd  47545 Aug  1 14:19 Medical history_2005.sav
-rwx------ 1 sfos0247 mkpasswd  50087 Aug  1 14:19 Medical history_2010.sav
-rwx------ 1 sfos0247 mkpasswd  23945 Aug  1 14:19 Medical history_2015.sav
-rwx------ 1 sfos0247 mkpasswd  12054 Aug  1 14:19 Participant HIV status.sav
-rwx------ 1 sfos0247 mkpasswd 134948 Aug  1 14:19 Physical measurements.sav
-rwx------ 1 sfos0247 mkpasswd  25648 Aug  2 09:28 Variables of interestFINAL.docx
-rwx------ 1 sfos0247 mkpasswd      0 Aug 10 18:47 data-raw-list.txt
```

Looks like "Combined data 2005_2010_2015.sav" is everything we need?

# 10.8.2017

Need to come up with standard variable names.

Go through `Variables of interestFINAL.docx` and prepare questions for Lanthe re data availability, and notes.


## Standard variable names

Use the ones in the .sav files, not our data request. They use undescores, but that's not a big deal.


# 11.8.2017

Prepare available variable summaries. 

## Available variables - missing 

Summary table of variables and proportion missing, total N = 2025. 
(plwh(a) is shorthand for "People with HIV/Aids")

This table needs to be paired with a verision of Sara and mine variable request table, also the order here is alphabetical. 

```{r, echo = FALSE}
dt <- read.csv("../data/outputs/combined.variables.missing.csv")
knitr::kable(dt, digits = 2)
```

## Codebook

The summary statistics for all 73 variables is in the appendix. 


# 14.8.2017

Merge our variable list with available list.. OK, realise that there are more variables than just in the 'combined file'. So will have to do a merge. 

# 15.8.2017

Merge all datafiles? 

Maybe not all, but how can I automate this without duplicating files already joined by Lanthe. 

Start 01-data-clean.R

OK, file list 


```{r, echo = FALSE}
rv.dt <- read.csv("../data/raw-data/requested-vars.csv")
received <- read.csv("../data/outputs/received.varnames.csv")

rv.dt %>% mutate(id = 1:nrow(rv.dt)) %>% 
  dplyr::rename(variables = VARIABLES ) %>% 
  dplyr::select(id, variables) %>% 
  mutate(year.2005 = NA, 
         year.2010 = NA,
         year.2015 = NA) %>% 
  as_tibble() %>% 
  rbind(list(0, "ID", NA, NA, NA), .) -> all.vars
all.vars[1,3:5] <- rep(received[1,2], 3)
all.vars[2,3:5] <- received[4:6,2]
all.vars[3,3:5] <- rep(received[3,2], 3)
all.vars[4,3:5] <- received[7:9,2]
all.vars[5,3:5] <- received[10:12,2]
all.vars[6,3:5] <- received[13:15,2]
all.vars[7,3:5] <- received[20:22,2]
all.vars[8,3:5] <- c(received[23,2], NA, NA)
all.vars <- rbind(all.vars, c(7.5,unlist(all.vars[8,2:5]))) %>% 
  mutate(id = as.numeric(id)) %>% arrange(id)
all.vars[9,3:5] <- received[44:46,2]

all.vars[18:28,]
received[24:35,]

```

## Notes

* in 2010 files there is an additional case #13020, check with Lanthe, but removed for now as presumably typo?
* in 2010 files there are three cases (3370, 1211 and 1486) that change gender, these are assumed to be typos. 

## Follow-up for Lanthe:

* Number of cases: There are 2021 in the 2005 demographic data file. How are there one more in the 2010 file?
* what is barcode # 13020 in `Combined data 2005_2010.sav data 2010.sav` and ` Demographic data 2010.sav `, `Live events_2010.sav` and `  Medical history_2010.sav `
* what is up with barcode # 3370? In  `Demographic data 2005.sav ` they are Female, in `Demographic data 2010.sav ` they are Male, in  `Demographic data 2015.sav ` they have no gender or location recorded. 
* what is up with barcode # 1211? In  `Demographic data 2005.sav ` they are Female, in `Demographic data 2010.sav ` they are Male, in  `Demographic data 2015.sav ` they are "2", which is presumably again female?
* what is up with barcode # 1486? In  `Demographic data 2005.sav ` they are Male, in `Demographic data 2010.sav ` they are Female, in  `Demographic data 2015.sav ` they are "1", which is presumably again male? 
* Additionally there are 16 (2184 2231 2312 2315 2325 3159 3166 3218 3254 4161 4219 4250 4301 4343 4381 4390) where the gender and location data are missing in 2010. Presumably it hasn't changed, but why the inconsistency?
* 2231 and 2315 have missing genders and most other demographic data in ``Demographic data 2010.sav ` but have other 2010 wave data? How come?

## Techincal points for Lanthe - no need for follow-up
*  `Demographic data 2015.sav` location and gender are not labeled. 



# Appendix - codebook 73 vars

Original 73 variables in original order

```{r, echo = FALSE,  message=FALSE, warning=FALSE, results='asis'}
require(memisc)
load("../data/outputs/combined.variables.codebook.RData")
combined.summary
```